Wireframe2DOM: From Static Graph to Responsive HTML

### 2020-05-01 document/paper.tex

\begin{document}
%
\title{Wireframe2DOM: From Static Graph to Responsive HTML}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Shangyin Tan\thanks{equal contribution} \and
Tiger Tang\printfnsymbol{1}}
%
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Purdue University\\
\email{\{tan279,tang426\}@purdue.edu}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Program Synthesis  \and Web Development \and User Interface}
\end{abstract}
%
%
%
\section{Introduction}
\section{Background}
\section{Related work}
\section{Illustrative example}
\section{Formal problem definition}
\section{Algorithm}
First we divide the rectangles into section based on their $y$-axis. Then we use
greedy to find the earlist possible cut $y$ such that this $y$ does not divide any
other rects.
\section{Evaluation}
\section{Conclusion}

%\subsection{A Subsection Sample}

% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.

% Subsequent paragraphs, however, are indented.

% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.

% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.

% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}

% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
% %
% % ---- Bibliography ----
% %
% % BibTeX users should specify bibliography style 'splncs04'.
% % References will then be sorted and formatted in the correct style.
% %
% % \bibliographystyle{splncs04}
% % \bibliography{mybibliography}
% %
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\end{document}

>>>>

\begin{document}
%
\title{Wireframe2DOM: From Static Graph to Responsive HTML}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Shangyin Tan\thanks{equal contribution} \and
Tiger Tang\printfnsymbol{1}}
%
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Purdue University\\
\email{\{tan279,tang426\}@purdue.edu}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We propose a lightweight program synthesizer that generates HTML from static Wireframe design graph.
With our program, a UI/UX designer with little or no programming experience can obtain responsive HTML from design layout.

\keywords{Program Synthesis  \and Web Development \and User Interface}
\end{abstract}
%
%
%
\section{Introduction}
Program synthesis community targets mainly on string processing and integer manipulating problem. However, the need for generating web application and other Graphical User Interface(GUI) applications is growing. While some UI/UX designers are capable of writing frontend code, providing them with a tool that generating HTML code can be beneficial. With HTML code equivalent to their interface design, designers can edit, test, and improve the original static layout. For example, many web applications now seek compatibility between PC and mobile devices. The different sizes complicate the designers' work. Some layouts are more promising on $16:9$ screen than on other smart devices. With the responsive HTML generated by our project, designer can preview the layout in a new resolution without re-drawing.

Our work focuses on configure the relationship between each atom elements in the static layout. We combine components of different sizes and locations into horizontal/vertical divisions and grids.  Instead of the absolute coordinate given by input, we assign margin to the converted structure and remember the relative position between them. Without the limitation of absolute coordinates, the converted structures can be rendered with the designers' true intention.

\section{Related work}
% Tiger

\section{Illustrative example}
% Shangyin
\section{Background}
% Shangyin
\section{Formal problem definition}
% Shangyin
\section{Algorithm}
% Shangyin
\subsection{Workflow}
Static Graph (the absolute location of each component) $=>$ relative intermediate representation $=>$HTML
\subsection{Grammar}
\subsubsection{Input}
RECT\\
RECTLIST:= RECTLIST RECT | Nil
\subsubsection{IR}
DIV\\
HDIV:= HDIV|DIV|VDIV\\
VDIV:= HDIV|DIV|VDIV\\
First we divide the rectangles into section based on their $y$-axis. Then we use
greedy to find the earliest possible cut $y$ such that this $y$ does not divide any
other rects.

\section{Evaluation}
% Tiger
\section{Conclusion}
% Tiger

\end{document}
